---
title: "p8105_hw1_hw2861"
output: github_document
date: "2022-09-17"
---

##Problem 1
I use the following code to load the penguins dataset

```{r }
data("penguins", package = "palmerpenguins")
names(penguins)
head(penguins)
summary(penguins)
nrow(penguins)
ncol(penguins)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

Discussion:

In Question1,I try to find the best way to display the penguins dataset.

I use "names(penguins)",so we can know that there are 8 variables.
They are "species","island","bill_length_mm","bill_depth_mm","flipper_length_mm","body_mass_g" and"sex"and"year".
Also, i use "summary(penguins)" to better estimate the distribution of these 8 variables.
From the important variables like "Species" or "Island",
We learned that there are three species of penguins (Adelie,Chinstrap and Gentoo) in the dataset from the three islands(Biscoe,Dream and Torgersen).
Again, by using "summary(penguins)", we can know the distribution of bill size and flipper length, and body mass of these penguins.The mean flipper length of the dataset is 200.92mm. The mean bill length is 43.92mm. And the mean bill depth is 17.15mm.
I also used "head(penguins)" because it is the recommended ways to show the dataset in the GitHub documentation.

There are 344 rows and 8 cols in this dataset.




Make a scatterplot
```{r}
library(ggplot2)
ggplot(data=penguins,aes(x = bill_length_mm, y = flipper_length_mm,color=species))+ geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 5)
```



##Problem 2

X1 is the random sample
x2 is the logical vector
x3 is the character vector
x4 is the factor vector

```{r}
library(tidyverse)
example_df = tibble(
x1 = rnorm(10),
x2 = x1 > 0,
x3= c("a","b","c","d","e","f","g","h","i","k"),
x4 = factor(c("Small", "Medium", "Small", "Small","Large", "Large", "Medium","Large","Medium","Small"))
)
example_df
```


We take the mean of the variables

```{r}
mean_x1 = mean(pull(example_df,x1))
mean_x2 = mean(pull(example_df,x2))
mean_x3 = mean(pull(example_df,x3))
mean_x4 = mean(pull(example_df,x4))
```

The x1(a random sample) and x2(The logical vector) can be used to take the mean.
But the X3(character vector) and X4(factor vector) can Not be used to take the mean.


```{r,eval=FALSE}
### convert logical vector into numeric vector
pull(example_df,x2)
x2_num = as.numeric(example_df$x2)
mean(x2_num)
### convert character vector into numeric vector
pull(example_df,x3)
x2_num = as.numeric(example_df$x3)
mean(x3_num)
### convert factor vector into numeric vector
pull(example_df,x4)
x2_num = as.numeric(example_df$x4)
mean(x4_num)
```

Based on the console,
we can not convert character vector and factor vector into numeric vector.
Because the elements in character and factor can not be treated like a certain number or value.

Bue the logical vector can be converted into numeric value.
Since the True or False can be converted into " 1 or 0"

This helps me to explain what happens before when i try to take the mean.
As long as this vector can be converted into numeric vector, 
(The elements in the vector can be treated like numeric value)
then we can calculate the mean value.


