---
title: "p8105_hw1_hw2861"
output: github_document
date: "2022-09-17"
---

Problem 1
I use the following code to load the penguins dataset

```{r }
data("penguins", package = "palmerpenguins")
names(penguins)
summary(penguins)
penguins
nrow(penguins)
ncol(penguins)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

Based on the R outcome,
There are 8 variables(ncol),they are 
"species",
"island",
"bill_length_mm",
"bill_depth_mm",
"flipper_length_mm",
"body_mass_g",
"sex"and"year".


Also,There are 344(nrow) individuals in this dataset.
The mean flipper length of the dataset is 200.92.


Make a scatterplot
```{r}
library(ggplot2)
ggplot(data=penguins,aes(x = bill_length_mm, y = flipper_length_mm,color=species))+ geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 5)
```




Problem 2

X1 is the random sample
x2 is the logical vector
x3 is the character vector
x4 is the factor vector

```{r}
example_df = tibble(
x1 = rnorm(10),
x2 = x1 > 0,
x3= c("a","b","c","d","e","f","g","h","i","k"),
x4 = factor(c("Small", "Medium", "Small", "Small","Large", "Large", "Medium","Large","Medium","Small"))
)
example_df
```


We take the mean of the variables

```{r}
library(tidyverse)
mean_x1 = mean(pull(example_df,x1))
mean_x2 = mean(pull(example_df,x2))
mean_x3 = mean(pull(example_df,x3))
mean_x4 = mean(pull(example_df,x4))
```

The x1(a random sample) and x2(The logical vector) can be used to take the mean.
But the X3(character vector) and X4(factor vector) can Not be used to take the mean.


```{r}
### convert logical vector into numeric vector
pull(example_df,x2)
x2_num = as.numeric(example_df$x2)
mean(x2_num)

### convert character vector into numeric vector
pull(example_df,x3)
x2_num = as.numeric(example_df$x3)
mean(x3_num)

### convert factor vector into numeric vector
pull(example_df,x4)
x2_num = as.numeric(example_df$x4)
mean(x4_num)
```

Based on the console,
we can not convert character vector and factor vector into numeric vector.
Because the elements in character and factor can not be treated like a certain number or value.

Bue the logical vector can be converted into numeric value.
Since the True or False can be converted into " 1 or 0"

This helps me to explain what happens before when i try to take the mean.
As long as this vector can be converted into numeric vector, 
(The elements in the vector can be treated like numeric value)
then we can calculate the mean value.
