---
title: "p8105_hw1_hw2861"
output: github_document
date: "2022-09-17"
---

Problem 1
I use the following code to load the penguins dataset

```{r }
data("penguins", package = "palmerpenguins")
names(penguins)
summary(penguins)
penguins
nrow(penguins)
ncol(penguins)
mean(penguins$flipper_length_mm, na.rm = TRUE)
```

Based on the R outcome,
There are 8 variables(ncol),they are 
"species","island","bill_length_mm","bill_depth_mm","flipper_length_mm","body_mass_g","sex"and"year".
Also,There are 344(nrow) individuals in this dataset.
The mean flipper length of the dataset is 200.92.



Make a scatterplot
```{r}
library(ggplot2)
ggplot(data=penguins,aes(x = bill_length_mm, y = flipper_length_mm,color=species))+ geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 5)
```




Problem 2

X1 is the random sample
x2 is the logical vector
x3 is the character vector
x4 is the factor vector

```{r}
example_df = tibble(
x1 = rnorm(10),
x2 = x1 > 0,
x3= c("a","b","c","d","e","f","g","h","i","k"),
x4 = factor(c("Small", "Medium", "Small", "Small","Large", "Large", "Medium","Large","Medium","Small"))
)
example_df
```


We take the mean of the variables

```{r}
library(tidyverse)
mean_x1 = mean(pull(example_df,x1))
mean_x2 = mean(pull(example_df,x2))
mean_x3 = mean(pull(example_df,x3))
mean_x4 = mean(pull(example_df,x4))
```
