---
title: "p8105_hw1_hw2861"
author: "Hongmiao Wang"
output: github_document
date: "2022-09-17"
---

##Problem 1
I use the following code to load the penguins dataset

```{r }
data("penguins", package = "palmerpenguins")
#Show the names of the variables
names(penguins)
#Display the dataset
head(penguins)
#Check the distribution of the variables
summary(penguins)
#Check the size of the dataset
nrow(penguins)
ncol(penguins)
#Check the mean flipper length
mean(penguins$flipper_length_mm, na.rm = TRUE)
```



The short description using inline R code:

This is a dataset containing information about penguins.
For the size of the datasize, There are `r nrow(penguins)` rows and `r ncol(penguins)` cols.
Meaning that `r nrow(penguins)`  penguins were included in the dataset and for each penguin we had `r ncol(penguins)` study variables.
The 8 variables in the Penguins dataset are `r names(penguins)`.
From the important variables like "Species" or "Island",
We learned that there are three species of penguins (Adelie,Chinstrap and Gentoo) in the dataset from the three islands(Biscoe,Dream and Torgersen).We can also know the distribution of bill Depth/Length and flipper length, body mass,the sex of these penguins.
We can use the mean value to estimate some important variables.
The mean flipper length of the penguins is `r mean(penguins$flipper_length_mm, na.rm = TRUE)`mm. 
The mean body mass is  `r mean(penguins$body_mass_g, na.rm = TRUE)`g.
The mean bill length and bill depth are `r mean(penguins$bill_length_mm, na.rm = TRUE)`mm and `r mean(penguins$bill_depth_mm, na.rm = TRUE)`mm respectively.
The data are collected from `r min(penguins$year, na.rm = TRUE)` to `r max(penguins$year, na.rm = TRUE)`.


Make a scatterplot
```{r}
library(ggplot2)
ggplot(data=penguins,aes(x = bill_length_mm, y = flipper_length_mm,color=species))+ geom_point()
ggsave("scatter_plot.pdf", height = 4, width = 5)
```



##Problem 2

X1 is the random sample
x2 is the logical vector
x3 is the character vector
x4 is the factor vector

```{r}
library(tidyverse)
example_df = tibble(
x1 = rnorm(10),
x2 = x1 > 0,
x3= c("a","b","c","d","e","f","g","h","i","k"),
x4 = factor(c("Small", "Medium", "Small", "Small","Large", "Large", "Medium","Large","Medium","Small"))
)
example_df
```


We take the mean of the variables

```{r}
mean_x1 = mean(pull(example_df,x1))
mean_x2 = mean(pull(example_df,x2))
mean_x3 = mean(pull(example_df,x3))
mean_x4 = mean(pull(example_df,x4))
```

The x1(a random sample/Numeric vector) and x2(The logical vector) can be used to take the mean.
But the X3(character vector) and X4(factor vector) can Not be used to take the mean.


```{r,eval=FALSE}
### convert logical vector into numeric vector
pull(example_df,x2)
x2_num = as.numeric(example_df$x2)
mean(x2_num)
### convert character vector into numeric vector
pull(example_df,x3)
x3_num = as.numeric(example_df$x3)
mean(x3_num)
### convert factor vector into numeric vector
pull(example_df,x4)
x4_num = as.numeric(example_df$x4)
mean(x4_num)
```

Based on the console,
we can not convert character vector into numeric vector.
Because the elements in character can not be treated like a certain number.

But the logical vector can be converted into numeric value.
Since the True or False can be converted into " 1 or 0"

And the factor vector can also be converted into numeric value.
The value of "Small/Medium/Large" can be converted into " 3/2/1"


This helps me to explain what happens before when i try to take the mean.
As long as this vector can be converted into numeric vector, 
(The elements in the vector can be treated like numeric value)
then we can calculate the mean value.


